RAX:Efficiently Evaluating the Complexity of Porting for RISC-V

### 2024-01-30 Paper/paper.tex
Add files via upload

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  In recent years, the open-source and the advantages of reduced ISA of the RISC-V architecture are attracting active promotion of porting within the industry.Due to the lack of public available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, which is inefficient and time consuming. RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of software during porting for RISC-V.RAX provides precise evaluation solutions and builds a high-quality dataset for porting complexity,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-scenario C/C++ projects. The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://www.youtube.com/watch?v=SLphW3Ra4WM}{https://www.youtube.com/watch?v\\=SLphW3Ra4WM}.
\end{abstract}

@@

\subsection{Evaluation}
\subsubsection{Dataset}
 To evaluate RAX, We chose typical and popular C and C++ projects from upstream warehouse of the OpenEuler and GitHub\citep{stage2023}. First, we searched keywords "rv" or "riscv" and collected 139 projects as our training and testing dataset. Then, five postgraduate students are invited to tag the porting auxiliary for these projects. The evaluation scores are divided into three categories:low, medium, and high\citep{githubss}. Second, models are trained and tested based on the 139 projects. Third, to evaluate the RAX, additional 72 projects are collected and evaluated from GitHub. To gather response from developers, the community, forums, and emails were utilized. 
\subsubsection{Result and Analysis}
To solve the problem of unbalanced datasets and small sample datasets, we used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing.By comparing multiple indicators, we select the Random Forest, which had the highest accuracy of 0.857 as the classifier, as shown in Table \ref{tab:evaluation}.

>>>>

%%
%% The abstract is a short summary of the work to be presented in the
%% article.
\begin{abstract}
  In recent years, the open-source and the advantages of reduced ISA of the RISC-V architecture are attracting active promotion of porting within the industry.Due to the lack of public available standards for assessing software portability, the software porting process for the RISC-V architecture has been predominantly reliant on expert experience, which is inefficient and time consuming. RAX is a automated tool which aids the C/C++ programmer in evaluating  complexity of software during porting for RISC-V.RAX provides precise evaluation solutions and builds a high-quality dataset for porting complexity,enabling recommendations of suitable software with difficulty levels for developers of varying skill levels.We evaluate RAX on 72 popular and typical real-scenario C/C++ projects. The experimental result shows that 51 of them have been confirmed by developers within community.Interested users can explore the open-source implementation of RAX at \href{https://github.com/wangyuliu/RAX-2024}{https://github.com/wangyuliu/RAX-2024}, or watch the RAX video demo at \href{https://youtu.be/g_e4VhG4kkM}{https://youtu.be/g_e4VhG4kkM}.
\end{abstract}

@@

\subsection{Evaluation}
\subsubsection{Dataset}
 To evaluate RAX, We chose typical and popular C and C++ projects from upstream warehouse of the OpenEuler and GitHub\citep{stage2023}. First, we searched keywords "rv" or "riscv" and collected 139 projects as our training and testing dataset. Then, five postgraduate students are invited to tag the porting complexity for these projects. The evaluation scores are divided into three categories:low, medium, and high\citep{githubss}. Second, models are trained and tested based on the 139 projects. Third, to evaluate the RAX, additional 72 projects are collected and evaluated from GitHub. To gather response from developers, the community, forums, and emails were utilized. 
\subsubsection{Result and Analysis}
To solve the problem of unbalanced datasets and small sample datasets, we used ensemble learning methods \cite{6509481}, SMOTE \cite{4271036}, and random oversampling methods for data preprocessing\cite{5128907} addressing.By comparing multiple indicators, we select the Random Forest, which had the highest accuracy of 0.857 as the classifier, as shown in Table \ref{tab:evaluation}.
